---
title: "p8105_hw5_jz3425"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r, message = FALSE}
homicide = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
```

Discription: The raw data contains `r nrow(homicide)` cases of homicide in 50 large U.S. cities over the past decades.There are `r ncol(homicide)` variables including victim's name, location and time of the killing and whether an arrest was made.

Summarize within cities to obtain the total number of homicides and the number of unsolved homicides:
```{r}
homicide_df = 
  homicide %>% 
  unite("city_state", city:state)

homicide_total = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(total_number = n())

homicide_unsolved =
  homicide_df %>% 
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>% 
  group_by(city_state) %>% 
  summarize(unsolved_number = n())

homicide_summarize =
  left_join(homicide_total, homicide_unsolved, by = "city_state") %>% 
  mutate(unsolved_number = replace_na(unsolved_number, 0))
 
homicide_summarize %>% knitr::kable()
```

prop.test for Baltimore:

```{r, warning = FALSE}
prop_test_baltimore =
  prop.test(
    homicide_summarize %>% filter(city_state == "Baltimore_MD") %>% pull(unsolved_number),
    homicide_summarize %>% filter(city_state == "Baltimore_MD") %>% pull(total_number)
  )

prop_test_baltimore %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high) %>% 
  janitor::clean_names() %>% 
  knitr::kable(digit = 3)
```

run prop.test for each of the cities:

```{r, warning = FALSE}
prop_test_df = 
  homicide_summarize %>% 
  mutate(
    prop_test = map2(.x = unsolved_number, .y = total_number, ~ prop.test(x = .x, n = .y)),
    prop_test = map(prop_test, broom::tidy)
  ) %>% 
  unnest() %>% 
  select(city_state, total_number, unsolved_number, estimate, conf.low, conf.high) %>% 
  janitor::clean_names()

prop_test_df %>% knitr::kable(digit = 3)
```

Create a plot that shows the estimates and CIs for each city:

```{r, fig.height=8}
prop_test_df %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>% 
  ggplot(aes(y = city_state, x = estimate, fill = city_state)) +
  geom_col() +
  geom_errorbar(aes(xmin = conf_low, xmax = conf_high)) +
  theme(legend.position = "none") +
  labs(
    title = "Estimated unsolved proportion plot",
    x = "estimated unsolved proportion",
    y = "city"
  )
```

