---
title: "p8105_hw5_jz3425"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r, message = FALSE}
homicide = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
```

Discription: The raw data contains `r nrow(homicide)` cases of homicide in 50 large U.S. cities over the past decades.There are `r ncol(homicide)` variables including victim's name, location and time of the killing and whether an arrest was made.

Summarize within cities to obtain the total number of homicides and the number of unsolved homicides:
```{r}
homicide_df = 
  homicide %>% 
  unite("city_state", city:state)

homicide_total = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(total_number = n())

homicide_unsolved =
  homicide_df %>% 
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>% 
  group_by(city_state) %>% 
  summarize(unsolved_number = n())

homicide_summarize =
  left_join(homicide_total, homicide_unsolved, by = "city_state") %>% 
  mutate(unsolved_number = replace_na(unsolved_number, 0))
 
homicide_summarize %>% knitr::kable()
```

prop.test for Baltimore:

```{r, warning = FALSE}
prop_test_baltimore =
  prop.test(
    homicide_summarize %>% filter(city_state == "Baltimore_MD") %>% pull(unsolved_number),
    homicide_summarize %>% filter(city_state == "Baltimore_MD") %>% pull(total_number)
  )

prop_test_baltimore %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high) %>% 
  janitor::clean_names() %>% 
  knitr::kable(digit = 3)
```

run prop.test for each of the cities:

```{r, warning = FALSE}
prop_test_df = 
  homicide_summarize %>% 
  mutate(
    prop_test = map2(.x = unsolved_number, .y = total_number, ~ prop.test(x = .x, n = .y)),
    prop_test = map(prop_test, broom::tidy)
  ) %>% 
  unnest() %>% 
  select(city_state, total_number, unsolved_number, estimate, conf.low, conf.high) %>% 
  janitor::clean_names()

prop_test_df %>% knitr::kable(digit = 3)
```

Create a plot that shows the estimates and CIs for each city:

```{r, fig.height=8}
prop_test_df %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>% 
  ggplot(aes(y = city_state, x = estimate, fill = city_state)) +
  geom_col() +
  geom_errorbar(aes(xmin = conf_low, xmax = conf_high)) +
  theme(legend.position = "none") +
  labs(
    title = "Estimated unsolved proportion plot",
    x = "estimated unsolved proportion",
    y = "city"
  )
```

## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

```{r, message = FALSE}
list_files = list.files("data", full.names = TRUE)

df = 
  map(list_files, read_csv) %>% 
  bind_rows()

df =
  df %>% 
  mutate(
    name = list.files("data"),
    name = substr(name, 1, 6)
    ) %>% 
  separate(name, into = c("arm", "id"), sep = "_") %>% 
  mutate(
    id = as.numeric(id)
  ) %>% 
  select(id, arm, everything()) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation"
  )

df
```

Make a spaghetti plot showing observations on each subject over time:

```{r}
df %>% 
  mutate(id = factor(id)) %>% 
  ggplot(aes(x = week, y = observation, color = arm)) +
  geom_point() +
  geom_line(aes(group = interaction(id, arm)))
```

Apparently, observations of experimental groups are higher than those of control groups. In general, observations of experimental groups have a increasing trend over weeks, while control groups seem relatively steady.

## Problem 3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()

fill_in = function(x) {
  
  if (is.numeric(x)) {
    mean = mean(x, na.rm = TRUE)
    x = replace_na(x, mean)
  } else {
    x = replace_na(x, "virginica")
  }
  
  x
  
}

iris_fill = map_dfr(iris_with_missing, fill_in)

iris_fill %>% knitr::kable(digit = 1)
```

